**Dynamics of Epiphytic Microbial Communities on Marine Macrophyte Surfaces**

### 2020-01-31 submission/manuscript.Rmd
Switch to Silva database v138.

### Sequence Analysis
```{r}
# Calculation of the error rate based on the ATCC MSA-1002 mock community
error <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.pick.error.summary", na="") %>%
  filter(numparents==1) %>%
  mutate(mismatches_weight=weight*mismatches) %>%
  mutate(total_weight=weight*total)
error <- sum(error$mismatches_weight)/sum(error$total_weight)*100
# Calculation of the number of sequences in the negative control
nc <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.nr_v132.wang.tax.summary") %>%
  filter(taxon=="Root") %>%
  select(NC_1)
```
Obtained sequences were analyzed on the computer cluster Isabella (University Computing Center, University of Zagreb) using mothur (version 1.43.0) [@Schloss2009] according to the MiSeq Standard Operating Procedure (MiSeq SOP; https://mothur.org/wiki/MiSeq_SOP) [@Kozich2013] and recommendations given from the Riffomonas project to enhance data reproducibility (http://www.riffomonas.org/). For alignment and classification of sequences the SILVA SSU Ref NR 99 database (release 132; http://www.arb-silva.de) was used [@Quast2013; @Yilmaz2014]. Sequences classified as chloroplasts by mothur were exported, aligned using SILVA incremental aligner (SINA, version 1.6.0) [@Pruesse2012] against the same SILVA SSU Ref NR 99 database (release 132) and imported into ARB (version 6.0.6) [@Ludwig2004] for further phylogenetic analysis using the same database. Reference sequences close to imported ones were selected and used to calculate a phylogenetic tree using the Maximum Likelihood algorithm RAxML (version 7.0.3) with 1000 tree replicates [@Stamatakis2006]. Imported partial chloroplast sequences were added to the tree using the maximum parsimony criteria and not allowing changes to tree topology. Pipeline data processing and visualization was done using R (version 3.6.0) [@RCoreTeam2019], package tidyverse (version 1.2.1) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2019; @Zhu2019; @Allaire2019; @Xie2018]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (**TO BE ADDED LATER!**). Based on the ATCC MSA-1002 mock community included in the analysis a sequencing error rate of `r error` \si{\percent} was determined, which is in line with previously reported values for next-generation sequencing data [@Kozich2013; @Schloss2016]. In addition, the negative control processed together with the samples yielded only `r nc` sequences after sequence quality curation.

@@

\newpage
## Figures
\newpage
```{r out.width="100%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant bacterial sequences.\\label{community}", fig.pos="ht"}
include_graphics("../results/figures/community_barplot_phylum.jpg")
```

>>>>

### Sequence Analysis
```{r}
# Calculation of the error rate based on the ATCC MSA-1002 mock community
error <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.pick.error.summary", na="") %>%
  filter(numparents==1) %>%
  mutate(mismatches_weight=weight*mismatches) %>%
  mutate(total_weight=weight*total)
error <- sum(error$mismatches_weight)/sum(error$total_weight)*100
# Calculation of the number of sequences in the negative control
nc <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.nr_v138.wang.tax.summary") %>%
  filter(taxon=="Root") %>%
  select(NC_1)
```
Obtained sequences were analyzed on the computer cluster Isabella (University Computing Center, University of Zagreb) using mothur (version 1.43.0) [@Schloss2009] according to the MiSeq Standard Operating Procedure (MiSeq SOP; https://mothur.org/wiki/MiSeq_SOP) [@Kozich2013] and recommendations given from the Riffomonas project to enhance data reproducibility (http://www.riffomonas.org/). For alignment and classification of sequences the SILVA SSU Ref NR 99 database (release 132; http://www.arb-silva.de) was used [@Quast2013; @Yilmaz2014]. Sequences classified as chloroplasts by mothur were exported, aligned using SILVA incremental aligner (SINA, version 1.6.0) [@Pruesse2012] against the same SILVA SSU Ref NR 99 database (release 132) and imported into ARB (version 6.0.6) [@Ludwig2004] for further phylogenetic analysis using the same database. Reference sequences close to imported ones were selected and used to calculate a phylogenetic tree using the Maximum Likelihood algorithm RAxML (version 7.0.3) with 1000 tree replicates [@Stamatakis2006]. Imported partial chloroplast sequences were added to the tree using the maximum parsimony criteria and not allowing changes to tree topology. Pipeline data processing and visualization was done using R (version 3.6.0) [@RCoreTeam2019], package tidyverse (version 1.2.1) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2019; @Zhu2019; @Allaire2019; @Xie2018]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (**TO BE ADDED LATER!**). Based on the ATCC MSA-1002 mock community included in the analysis a sequencing error rate of `r error` \si{\percent} was determined, which is in line with previously reported values for next-generation sequencing data [@Kozich2013; @Schloss2016]. In addition, the negative control processed together with the samples yielded only `r nc` sequences after sequence quality curation.

@@

\newpage
## Figures
\newpage
```{r out.width="100%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant bacterial sequences.\\label{community}", fig.pos="ht"}
include_graphics("../results/figures/community_bar_plot.jpg")
```
